\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry}
    \usepackage{amsmath}
    \usepackage{hyperref}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
    % END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}

\vspace*{-40pt}

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Andrew Dudley}}\\
    2027 E. University Drive, Unit 131, Tempe, AZ, 85281\\
    Andrew.Dudley@asu.edu $\cdot$ (623) 910-0586\\

\end{center}

\vspace*{1mm}

%==== Education ====%
\header{Education}

\vspace{2mm}
\textbf{Arizona State University (Ira A. Fulton School of Engineering)}\hfill Tempe, AZ\\
    %\-\hspace{.7cm} \textbf{Master of Science in Computer Science}\hfill \textit{Expected May 2019} \\
    %\-\hspace{.7cm} \textbf{Bachelor of Science in Computer Science}\hfill Jan 2014 - May 2017\\
    %\-\hspace{.7cm} \textit{Summa Cum Laude} Cumulative GPA: 4.0/4.0
    \begin{itemize}
        \item Master of Science in Computer Science\hfill \textit{Expected May 2019} \\
            Cumulative GPA: 4.0/4.0
        \item Bachelor of Science in Computer Science\hfill Jan 2014 - May 2017\\
            \textit{Summa Cum Laude}, Cumulative GPA: 4.0/4.0
    \end{itemize}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\textbf{Yochan Artificial Intelligence Research Laboratory} \hfill Arizona State University\\
\textit{Research Assistantship - Supervised by  Dr. Subbarao Kambhampati} \hfill \\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Researching Vehicle-to-Vehicle (V2V) planning and communications for augmenting reality enabled smart HUDs to increase situational awareness of drivers
    \item Designed interface to collect human feedback on robot task plans using a simulated environment.
\end{itemize}
\textbf{Teaching Assistant} \hfill \\
\vspace{1mm}
\hspace{.5cm}$\bullet$ Artificial Intelligence \-  $\bullet$ Theoretical Computer Science \-$\bullet$ Principles of Programming Languages\\
\vspace{3mm}
\textbf{Data Mining and Machine Learning Laboratory} \hfill \\
\textit{Undergraduate Research Aide} \hfill Aug 2016 | Dec 2016\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed a distributed web scraping tool to mine data from Twitter hyperlinks (Python).
\end{itemize}

\textbf{Allstate} \hfill Chicago, IL\\
\textit{Application Developer Intern} \hfill May 2016 | Aug 2016\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Implemented natural language processing pipeline for chat bot, which included word sense disambiguation and concept mapping.
	\item Analyzed modern natural language processing solutions (SyntaxNet, NLTK, SpaCy).
\end{itemize}

\textbf{Rockwell Automation} \hfill Phoenix, AZ\\
\textit{Information Developer} \hfill Jan 2012 | Jul 2013\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Developed software solution to publish help documentation into a modern help viewer format.
	\item Created various tools for automating departmental and localization processes.
	\item Implemented feature requirements for online help and print deliverables (JavaScript, VBScript).
\end{itemize}

\header{Projects}
\textbf{An Investigation of Bounded Misclassification for Operational Security on Deep Neural Networks}
\begin{itemize}
    \item Implemented a neural network framework from scratch and trained models using domain-specific distance metrics in attempt to impose bounds on the misclassification rate of adversarial inputs.
\end{itemize}
\textbf{EpiFinder Tagging} (Capstone) \\
\begin{itemize}
       \item A biomedical text annotation tool that uses conditional random fields for named entity recognition to automatically tag ontological concepts. \textit {(Spring MVC, JavaScript, Java) }\\
\end{itemize}

\textbf{Allstate Intelligent Virtual Assistant Challenge} \\
    \textit{Automated chat client developed in Python}
    \begin{itemize}
        \item Awarded cash prize and summer internship at Allstate Headquarters in Chicago, IL.
        \item Chat bot designed to extract data from knowledge base articles and then use that knowledge to automatically assist users with technical issues and account updates.
        \item Pre-processing, tagging, and other NLP features implemented with Natural Language Toolkit.
        \end{itemize}
\vspace*{2mm}

\header{Skills}
\begin{tabular}{ l l }
	Programming: & Python, C, C++, C\#, Java                                                                      \\
	Web:         & Django, Spring MVC, JavaScript                                                                 \\
    Areas of Interest: & Reinforcement Learning, Deep Learning, Pattern Recognition
\end{tabular}
\end{document}
